### 2012-11-09 Docs/architecture/architecture.tex
a little more clarification on the boundary conditions for phi after chatting with Ann

{\tt ell\_bc\_level\_array} is the analog to {\tt
  adv\_bc\_level\_array} for the elliptic solves in \maestro.  This
will come into play in the multigrid portions of the code.  The
actions that are used for {\tt ell\_bc\_level\_array} are either
Dirichlet or Neumann boundary condtions.  For the velocity
projections, we are dealing with a pressure-like quantity, $\phi$, so
the pressure boundary conditions here reflect the behavior we want for
the velocity.  You want $d\phi/dn=0$ in places where the incoming
velocity to the elliptic solve must match the velocity you want after
the projection (e.g.\ inflow, solid walls).  For outlet boundaries,
setting $\phi = 0$ allows the velocity to adjust as needed to the
domain (see, for example, \cite{almgrenBellSzymczak:1996}).

>>>>

{\tt ell\_bc\_level\_array} is the analog to {\tt
  adv\_bc\_level\_array} for the elliptic solves in \maestro.  This
will come into play in the multigrid portions of the code.  The
actions that are used for {\tt ell\_bc\_level\_array} are either
Dirichlet or Neumann boundary condtions.  For the velocity
projections, we are dealing with a pressure-like quantity, $\phi$, so
the pressure boundary conditions here reflect the behavior we want for
the velocity.  After the projection, it is $\nabla \phi$ that modifies
the velocity field.  At a wall or for inflow conditions, we already
have the velocity we want at the boundary, so we want the velocity to
remain unchanged after the projection.  This requires $d\phi/dn=0$ on
those boundaries.  For outflow, we impose a condition that we do not
want the boundaries to introduce any tangental acceleration (or
shear), this is equivalent to setting $\phi = 0$ (then $\partial
\phi/d\partial t = 0$, with $t$ meaning `tangental').  This allows the
velocity to adjust as needed to the domain (see, for example,
\cite{almgrenBellSzymczak:1996}).
